Bioverse: Origins of Life

### 2024-05-29 src/tex/ms.tex
extend planet tracks

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample with \gls{EEC} highlighted in green.
        Two of the three planet trajectories shown have extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections), our requirement for abiogenesis.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\SI{}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$.
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
\begin{figure}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux -- biosignature occurrence space. The dashed line denotes the threshold \gls{NUV} flux $F_\mathrm{NUV, min}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure}

>>>>

\begin{figure*}
    \script{hz_nuv_evo.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hz_nuv_evo}
        \caption{Interpolated stellar luminosity evolution (left) and evolution of the \gls{NUV} flux in the \gls{HZ} as a function of host star mass. The scatter plot shows age and host star mass of the transiting planets in the synthetic sample.% with \gls{EEC} highlighted in green.
        We show the evolutionary tracks of a few randomly selected planets.
        Tracks with extended overlap of \gls{HZ} occupancy and high \gls{NUV} flux (green sections) fulfill our requirement for abiogenesis.}
        \label{fig:hz_nuv_evo}
    \end{centering}
\end{figure*}

@@

A representative recovery of the injected biosignature pattern is shown in Figure~\ref{fig:detections_uv}.
There, we assumed an abiogenesis rate of $f_\mathrm{life} = \var{f_life}$ and a minimum \gls{NUV} flux of $F_\mathrm{NUV, min} = \var{NUV_thresh}\,\SI{}{\photons\per\centi\meter\squared\per\second\per\nano\meter}$.
This leads to a distribution of biosignature detections with detections increasingly occurring above a threshold inferred NUV flux.
\begin{figure}
    \script{detections_uv.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/detections_uv}
        \caption{Recovered biosignature detections in the \gls{NUV} flux -- biosignature occurrence space. The dashed line denotes the threshold \gls{NUV} flux $F_\mathrm{NUV, min}$.}
        \label{fig:detections_uv}
    \end{centering}
\end{figure}
